Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-08 jss/article.tex
[skip ci] jss update

The package also includes a use-case that we detail below. Using, \code{genes_test} it is possible to explore the different possibilities of exploration of the maps. We previously computed the p-value of \code{genes_test} with default parameters.
The number of modules which have a p-value below 0.05 was 36, that can be compared to the 49 obtained without correction:
\code{enrichment(genes_test,correction_multitest = FALSE)}
\begin{table}[h!]
  \centering
  \caption{Overview of results from enrichment analysis without correction. Module : name of the module. Module size: size of the module. Genes in module: genes from input which are found in the module. p-value: uncorrected p-value. Test : null hypothesis used, greater is synonym of enrichment.}
  \label{tab:table2}

  \begin{tabular}{l|c|c|c|c}
	\hline
Module & Module size & Genes in module & p-value & Test\\
	\hline
Apoptosis:E2F1 & 5 &  ATM E2F1 EP300 KAT2B  & 1.043478e-08 & greater \\
Apoptosis:G2 M CHECKPOINT & 35  & ATM KAT2B & 2.040546e-02 & greater \\
Apoptosis:WNT CANONICAL & 53 & E2F1 EP300 KAT2B  & 4.984433e-03 & greater \\
	\end{tabular}
\end{table}

>>>>

The package also includes a use-case that we detail below. Using, \code{genes_test} it is possible to explore the different possibilities of exploration of the maps. We previously computed the p-value of \code{genes_test} with default parameters.
The number of modules which have a p-value below 0.05 was 36, that can be compared to the 49 obtained without correction:
\code{enrichment(genes_test,correction_multitest = FALSE)}
\begin{table}[h!]
  \centering
  \caption{Overview of results from enrichment analysis without correction. Module : name of the module. Mod. size: size of the module. Genes in module: genes from input which are found in the module. p-value: uncorrected p-value. Test : null hypothesis used, greater is synonym of enrichment.}
  \label{tab:table2}

  \begin{tabular}{l|c|c|c|c}
	\hline
Module & Mod. size & Genes in module & p-value & Test\\
	\hline
Apoptosis:E2F1 & 5 &  ATM E2F1 EP300 & 1.04e-08 & greater \\
               &   &  KAT2B                 &          &         \\
Apoptosis:G2 M CHECKPOINT & 35  & ATM KAT2B & 2.04e-02 & greater \\
Apoptosis:WNT CANONICAL & 53 & E2F1 EP300 KAT2B  & 4.98e-03 & greater \\
	\end{tabular}
\end{table}
